### 2019-04-25 Chapters/Chapter4.tex
more spaces

\chapter{Perturbing the lattice}
\label{ChapPerturbing}

@@

\begin{equation*}
\hat{H} = -t_0\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
\end{equation*}

In this model, since SOI is not taken into account, only the exchange interaction $J$ plays a role. The electromagnetic perturbation is then introduced via the Peierls substitution. We reproduce the result in section \ref{Section3Hubbard}. In the following sections we extend the analysis to different systems with spin orbit interaction thereby modulating $\bs{D}_{ij}$ or other spin interactions. The simplest model with spin orbit interaction is \ref{Hubbard}:

\begin{equation*}
\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{0} + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
\end{equation*}

Which is the same Hubbard model plus a spin dependent hopping term, which represents Rashba SOI for $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^y, -R_{ij}^x, 0)$ or Dresselhaus SOI for $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^x, -R_{ij}^y, 0)$. In section \ref{Section3HubbardSOI} we show how the exchange interaction and the DMI couplings are modulated in presence of an electromagnetic field.

>>>>

\chapter{Laser illumination}
\label{ChapPerturbing}

@@

\begin{equation*}
\hat{H} = -t_0\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
\end{equation*} 
In this model, since SOI is not taken into account, only the exchange interaction $J$ plays a role. The electromagnetic perturbation is then introduced via the Peierls substitution. We reproduce the result in section \ref{Section3Hubbard}. In the following sections we extend the analysis to different systems with spin orbit interaction thereby modulating $\bs{D}_{ij}$ or other spin interactions. The simplest model with spin orbit interaction is \ref{Hubbard}:

\begin{equation*}
\hat{H} = -\sum_{\langle i,j \rangle, \sigma, \sigma'}(\delta_{\sigma, \sigma'} t_{0} + \bs{\Delta}_{ij} \bs{\sigma}_{\sigma, \sigma'})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma'} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}
\end{equation*}
Which is the same Hubbard model plus a spin dependent hopping term, which represents Rashba SOI for $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^y, -R_{ij}^x, 0)$ or Dresselhaus SOI for $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^x, -R_{ij}^y, 0)$. In section \ref{Section3HubbardSOI} we show how the exchange interaction and the DMI couplings are modulated in presence of an electromagnetic field.
